---
title: "BrICC Student Data"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    source_code: embed
    vertical_layout: scroll
    theme: cerulean
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(rio)
library(here)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)

opts_chunk$set(echo = FALSE,
               fig.width = 5,
               fig.height = 6)

theme_set(theme_minimal(base_size = 8))

bricc <- import(here("data", "bricc_data_new.sav"),
               setclass = "tbl_df") %>% 
  characterize() %>% 
  janitor::clean_names() 

head(bricc)
```

# Winter 2020

Column {.tabset data-width=650}
-----------------------------------------------------------------------

### Quiz Score Table 
```{r total score winter 2020 data cleaning, include=FALSE}

winter_2020 <- bricc %>% 
  filter(term == 2)

winter_2020_score_table <- winter_2020 %>% 
  select(student_name, 
         pre_test_total_score, 
         post_test_total_score, 
         pre_test_knowledge_score, 
         post_test_knowledge_score, 
         pre_test_application_score, 
         post_test_application_score) %>% 
  rename("Student Name" = student_name,
         "Pre-Test Total Score" = pre_test_total_score,
         "Post-Test Total Score" = post_test_total_score,
         "Pre-Test Knowledge Score" = pre_test_knowledge_score,
         "Post-Test Knowledge Score" = post_test_knowledge_score,
         "Pre-Test Application Score" = pre_test_application_score,
         "Post-Test Application Score" = post_test_application_score)

winter_2020 <- winter_2020 %>% 
  rename("Pre-Test Total Score" = pre_test_total_score,
         "Post-Test Total Score" = post_test_total_score,
         "Pre-Test Knowledge Score" = pre_test_knowledge_score,
         "Post-Test Knowledge Score" = post_test_knowledge_score,
         "Pre-Test Application Score" = pre_test_application_score,
         "Post-Test Application Score" = post_test_application_score)

winter_2020_tidy_quiz <- winter_2020 %>% 
  pivot_longer(
    cols = c(`Pre-Test Total Score`,
             `Post-Test Total Score`,
             `Pre-Test Knowledge Score`,
             `Post-Test Knowledge Score`,
             `Pre-Test Application Score`,
             `Post-Test Application Score`),
    names_to = "assessment",
    values_to = "score"
  )

```

```{r total score winter 2020}

reactable(winter_2020_score_table)
```

### Quiz Score Plot 
```{r quiz winter 2020 plot data cleaning, include=FALSE}


winter_2020_tidy_quiz$assessment <- factor(winter_2020_tidy_quiz$assessment, 
                                     levels = c("Post-Test Total Score",
                                                "Pre-Test Total Score",
                                                "Post-Test Knowledge Score",
                                                "Pre-Test Knowledge Score",
                                                "Post-Test Application Score",
                                                "Pre-Test Application Score"))

```

```{r quiz plot winter 2020, fig.width=7, fig.height=6.5}
ggplot(winter_2020_tidy_quiz, aes(assessment, score)) +
  geom_col(fill = "blue", 
           alpha = 0.7) +
  coord_flip() +
  geom_text(aes(assessment, score, label = score),
            nudge_y = -0.5,
            color = "white") +
  facet_wrap(~student_name) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(color = "gray80")) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(plot.title = element_text(color = "black", size = 12, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10),
        axis.title=element_text(size=10),
        strip.text = element_text(size = 10)) +
  labs(x = "",
       y = "Score",
       title = "BrICC Winter 2020 Student Scores") 
```

### Survey Question 1

I am confident in my ability to conduct a consultation for the BrICC clinic

```{r survey question 1 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q1 <- winter_2020 %>% 
  select(student_name, pre_survey_q1, post_survey_q1) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q1,
         "Post-Survey Response" = post_survey_q1)

```

```{r question 1 winter 2020}

reactable(winter_2020_pre_post_q1)
```

### Survey Question 2

I am confident in my ability to administer standardized cognitive tests

```{r survey question 2 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q2 <- winter_2020 %>% 
  select(student_name, pre_survey_q2, post_survey_q2) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q2,
         "Post-Survey Response" = post_survey_q2)

```

```{r question 2 winter 2020}

reactable(winter_2020_pre_post_q2)
```


### Survey Question 3

I am confident in my ability to conduct a client-centered clinical interview

```{r survey question 3 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q3 <- winter_2020 %>% 
  select(student_name, pre_survey_q3, post_survey_q3) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q3,
         "Post-Survey Response" = post_survey_q3)

```

```{r question 3 winter 2020}

reactable(winter_2020_pre_post_q3)
```

### Survey Question 4

I am confident in my ability to identify treatment options to assist people with acquired cognitive impairments

```{r survey question 4 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q4 <- winter_2020 %>% 
  select(student_name, pre_survey_q4, post_survey_q4) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q4,
         "Post-Survey Response" = post_survey_q4)

```

```{r question 4 winter 2020}

reactable(winter_2020_pre_post_q4)
```

### Survey Question 5

I am prepared to write cognitive rehabilitation goals

```{r survey question 5 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q5 <- winter_2020 %>% 
  select(student_name, pre_survey_q5, post_survey_q5) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q5,
         "Post-Survey Response" = post_survey_q5)

```

```{r question 5 winter 2020}

reactable(winter_2020_pre_post_q5)
```

### Survey Question 6

I am prepared to administer direct interventions such as attention training or goal management training
```{r survey question 6 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q6 <- winter_2020 %>% 
  select(student_name, pre_survey_q6, post_survey_q6) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q6,
         "Post-Survey Response" = post_survey_q6)

```

```{r question 6 winter 2020}

reactable(winter_2020_pre_post_q6)
```

### Survey Question 7

I am prepared to engage in systematic instruction to support the use of external aids
```{r survey question 7 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q7 <- winter_2020 %>% 
  select(student_name, pre_survey_q7, post_survey_q7) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q7,
         "Post-Survey Response" = post_survey_q7)

```

```{r question 7 winter 2020}

reactable(winter_2020_pre_post_q7)
```

### Survey Question 8

I am prepared to engage in a needs assessment to identify cognitive strategies and support learning and use of them
```{r survey question 8 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q8 <- winter_2020 %>% 
  select(student_name, pre_survey_q8, post_survey_q8) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q8,
         "Post-Survey Response" = post_survey_q8)

```

```{r question 8 winter 2020}

reactable(winter_2020_pre_post_q8)
```

### Survey Question 9

I am confident in my ability to collect and analyze client session data
```{r survey question 9 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q9 <- winter_2020 %>% 
  select(student_name, pre_survey_q9, post_survey_q9) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q9,
         "Post-Survey Response" = post_survey_q9)
```

```{r question 9 winter 2020}

reactable(winter_2020_pre_post_q9)
```

### Survey Question 10

I am prepared to justify my decisions related to assessment and treatment selection
```{r survey question 10 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q10 <- winter_2020 %>% 
  select(student_name, pre_survey_q10, post_survey_q10) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q10,
         "Post-Survey Response" = post_survey_q10)

```

```{r question 10 winter 2020}

reactable(winter_2020_pre_post_q10)
```

### Survcey Question 11

I am confident in my ability to apply principles of evidence-based practice to my assessment and treatment decisions
```{r survey question 11 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q11 <- winter_2020 %>% 
  select(student_name, pre_survey_q11, post_survey_q11) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q11,
         "Post-Survey Response" = post_survey_q11)

```

```{r question 11 winter 2020}

reactable(winter_2020_pre_post_q11)
```


### Survey Question 12

I am confident in my ability to make ‘online’ (in session) changes to my daily plans
```{r survey question 12 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q12 <- winter_2020 %>% 
  select(student_name, pre_survey_q12, post_survey_q12) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q12,
         "Post-Survey Response" = post_survey_q12)

```

```{r question 12 winter 2020}

reactable(winter_2020_pre_post_q12)
```


### Survey Question 13

I am knowledgeable about concussion management
```{r survey question 13 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q13 <- winter_2020 %>% 
  select(student_name, pre_survey_q13, post_survey_q13) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q13,
         "Post-Survey Response" = post_survey_q13)

```

```{r question 13 winter 2020}

reactable(winter_2020_pre_post_q13)
```

### Survey Question 14

I am comfortable working with clients with brain injuries
```{r survey question 14 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q14 <- winter_2020 %>% 
  select(student_name, pre_survey_q14, post_survey_q14) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q14,
         "Post-Survey Response" = post_survey_q14)

```

```{r question 14 winter 2020}

reactable(winter_2020_pre_post_q14)
```

### Survey Question 15

I am comfortable working with clients with awareness deficits
```{r survey question 15 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q15 <- winter_2020 %>% 
  select(student_name, pre_survey_q15, post_survey_q15) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q15,
         "Post-Survey Response" = post_survey_q15)

```

```{r question 15 winter 2020}

reactable(winter_2020_pre_post_q15)
```

### Survecy Question 16

I am able to use case history information (e.g., information about etiology) to guide my clinical decision making
```{r survey question 16 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q16 <- winter_2020 %>% 
  select(student_name, pre_survey_q16, post_survey_q16) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q16,
         "Post-Survey Response" = post_survey_q16)

```

```{r question 16 winter 2020}

reactable(winter_2020_pre_post_q16)
```

### Survey Question 17

I feel prepared to orally present cases
```{r survey question 17 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q17 <- winter_2020 %>% 
  select(student_name, pre_survey_q17, post_survey_q17) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q17,
         "Post-Survey Response" = post_survey_q17)

```

```{r question 17 winter 2020}

reactable(winter_2020_pre_post_q17)
```


### Survey Question 18

Training was systematic and well organized (Post-Survey Only)
```{r survey question 18 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q18 <- winter_2020 %>% 
  select(student_name, post_survey_q18) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q18)

```

```{r question 18 winter 2020}

reactable(winter_2020_pre_post_q18)
```

### Survey Question 19

Group meetings enhanced my learning (Post-Survey Only)
```{r survey question 19 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q19 <- winter_2020 %>% 
  select(student_name, post_survey_q19) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q19)

```

```{r question 19 winter 2020}

reactable(winter_2020_pre_post_q19)
```


### Survey Question 20

Group meetings were efficient (Post-Survey Only)
```{r survey question 20 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q20 <- winter_2020 %>% 
  select(student_name, post_survey_q20) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q20)

```

```{r question 20 winter 2020}

reactable(winter_2020_pre_post_q20)
```


### Survey Question 21

Group meetings exposed me to learning about other client profiles and case management techniques (Post-Survey Only)
```{r survey question 21 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q21 <- winter_2020 %>% 
  select(student_name, post_survey_q21) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q21)

```

```{r question 21 winter 2020}

reactable(winter_2020_pre_post_q21)
```


### Survey Question 22

I learned enough about treatment approaches implemented by my peers to be able to implement them with a client even though I never personally delivered the intervention (Post-Survey Only)
```{r survey question 22 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q22 <- winter_2020 %>% 
  select(student_name, post_survey_q22) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q22)

```

```{r question 22 winter 2020}

reactable(winter_2020_pre_post_q22)
```


### Survey Question 23

I was exposed to clients with the same disorder/diagnosis with different manifestations or treatment needs (Post-Survey Only)
```{r survey question 23 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q23 <- winter_2020 %>% 
  select(student_name, post_survey_q23) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q23)

```

```{r question 23 winter 2020}

reactable(winter_2020_pre_post_q23)
```

### Survey Question 24

My supervisor supported my case management and clinical approach (Post-Survey Only)
```{r survey question 24 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q24 <- winter_2020 %>% 
  select(student_name, post_survey_q24) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q24)

```

```{r question 24 winter 2020}

reactable(winter_2020_pre_post_q24)
```


### Survey Question 25

(If you have already taken cognitive rehabilitation course) Because of this clinical experience, I am now able to apply theoretical knowledge and principles in a clinically sound matter (Post-Survey Only)
```{r survey question 25 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q25 <- winter_2020 %>% 
  select(student_name, post_survey_q25) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q25)

```

```{r question 25 winter 2020}

reactable(winter_2020_pre_post_q25)
```


### Survey Question 26

(If you have already taken cognitive rehabilitation course) I had the appropriate knowledge of theories and practice from my coursework to apply to this clinical experience (Post-Survey Only)
```{r survey question 26 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q26 <- winter_2020 %>% 
  select(student_name, post_survey_q26) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q26)

```

```{r question 26 winter 2020}

reactable(winter_2020_pre_post_q26)
```


### Survey Question 27

(If you have not yet taken cognitive rehabilitation course) I feel more prepared about enrolling in class because of this clinical experience (Post-Survey Only)
```{r survey question 27 winter 2020 data cleaning, include=FALSE}

winter_2020_pre_post_q27 <- winter_2020 %>% 
  select(student_name, post_survey_q27) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q27)

```

```{r question 27 winter 2020}

reactable(winter_2020_pre_post_q27)
```


# Spring 2020

Column {.tabset data-width=650}
-----------------------------------------------------------------------

### Quiz Score Table 
```{r total score spring 2020 data cleaning, include=FALSE}

spring_2020 <- bricc %>% 
  filter(term == 3)

spring_2020_score_table <- spring_2020 %>% 
  select(student_name, 
         pre_test_total_score, 
         post_test_total_score, 
         pre_test_knowledge_score, 
         post_test_knowledge_score, 
         pre_test_application_score, 
         post_test_application_score) %>% 
  rename("Student Name" = student_name,
         "Pre-Test Total Score" = pre_test_total_score,
         "Post-Test Total Score" = post_test_total_score,
         "Pre-Test Knowledge Score" = pre_test_knowledge_score,
         "Post-Test Knowledge Score" = post_test_knowledge_score,
         "Pre-Test Application Score" = pre_test_application_score,
         "Post-Test Application Score" = post_test_application_score)

spring_2020 <- spring_2020 %>% 
  rename("Pre-Test Total Score" = pre_test_total_score,
         "Post-Test Total Score" = post_test_total_score,
         "Pre-Test Knowledge Score" = pre_test_knowledge_score,
         "Post-Test Knowledge Score" = post_test_knowledge_score,
         "Pre-Test Application Score" = pre_test_application_score,
         "Post-Test Application Score" = post_test_application_score)


spring_2020_tidy_quiz <- spring_2020 %>% 
  pivot_longer(
    cols = c(`Pre-Test Total Score`,
             `Post-Test Total Score`,
             `Pre-Test Knowledge Score`,
             `Post-Test Knowledge Score`,
             `Pre-Test Application Score`,
             `Post-Test Application Score`),
    names_to = "assessment",
    values_to = "score"
  )

```

```{r total score spring 2020}

reactable(spring_2020_score_table)
```

### Quiz Score Plot 
```{r quiz spring 2020 plot data cleaning, include=FALSE}


spring_2020_tidy_quiz$assessment <- factor(spring_2020_tidy_quiz$assessment, 
                                     levels = c("Post-Test Total Score",
                                                "Pre-Test Total Score",
                                                "Post-Test Knowledge Score",
                                                "Pre-Test Knowledge Score",
                                                "Post-Test Application Score",
                                                "Pre-Test Application Score"))

```

```{r quiz plot spring 2020, fig.width=7, fig.height=6.5}
ggplot(spring_2020_tidy_quiz, aes(assessment, score)) +
  geom_col(fill = "blue", 
           alpha = 0.7) +
  coord_flip() +
  geom_text(aes(assessment, score, label = score),
            nudge_y = -0.5,
            color = "white") +
  facet_wrap(~student_name) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(color = "gray80")) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(plot.title = element_text(color = "black", size = 12, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10),
        axis.title=element_text(size=10),
        strip.text = element_text(size = 10)) +
  labs(x = "",
       y = "Score",
       title = "BrICC Spring 2020 Student Scores") 
```

### Survey Question 1

I am confident in my ability to conduct a consultation for the BrICC clinic

```{r survey question 1 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q1 <- spring_2020 %>% 
  select(student_name, pre_survey_q1, post_survey_q1) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q1,
         "Post-Survey Response" = post_survey_q1)

```

```{r question 1 spring 2020}

reactable(spring_2020_pre_post_q1)
```

### Survey Question 2

I am confident in my ability to administer standardized cognitive tests

```{r survey question 2 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q2 <- spring_2020 %>% 
  select(student_name, pre_survey_q2, post_survey_q2) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q2,
         "Post-Survey Response" = post_survey_q2)

```

```{r question 2 spring 2020}

reactable(spring_2020_pre_post_q2)
```


### Survey Question 3

I am confident in my ability to conduct a client-centered clinical interview

```{r survey question 3 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q3 <- spring_2020 %>% 
  select(student_name, pre_survey_q3, post_survey_q3) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q3,
         "Post-Survey Response" = post_survey_q3)

```

```{r question 3 spring 2020}

reactable(spring_2020_pre_post_q3)
```

### Survey Question 4

I am confident in my ability to identify treatment options to assist people with acquired cognitive impairments

```{r survey question 4 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q4 <- spring_2020 %>% 
  select(student_name, pre_survey_q4, post_survey_q4) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q4,
         "Post-Survey Response" = post_survey_q4)

```

```{r question 4 spring 2020}

reactable(spring_2020_pre_post_q4)
```

### Survey Question 5

I am prepared to write cognitive rehabilitation goals

```{r survey question 5 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q5 <- spring_2020 %>% 
  select(student_name, pre_survey_q5, post_survey_q5) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q5,
         "Post-Survey Response" = post_survey_q5)

```

```{r question 5 spring 2020}

reactable(spring_2020_pre_post_q5)
```

### Survey Question 6

I am prepared to administer direct interventions such as attention training or goal management training
```{r survey question 6 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q6 <- spring_2020 %>% 
  select(student_name, pre_survey_q6, post_survey_q6) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q6,
         "Post-Survey Response" = post_survey_q6)

```

```{r question 6 spring 2020}

reactable(spring_2020_pre_post_q6)
```

### Survey Question 7

I am prepared to engage in systematic instruction to support the use of external aids
```{r survey question 7 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q7 <- spring_2020 %>% 
  select(student_name, pre_survey_q7, post_survey_q7) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q7,
         "Post-Survey Response" = post_survey_q7)

```

```{r question 7 spring 2020}

reactable(spring_2020_pre_post_q7)
```

### Survey Question 8

I am prepared to engage in a needs assessment to identify cognitive strategies and support learning and use of them
```{r survey question 8 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q8 <- spring_2020 %>% 
  select(student_name, pre_survey_q8, post_survey_q8) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q8,
         "Post-Survey Response" = post_survey_q8)

```

```{r question 8 spring 2020}

reactable(spring_2020_pre_post_q8)
```

### Survey Question 9

I am confident in my ability to collect and analyze client session data
```{r survey question 9 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q9 <- spring_2020 %>% 
  select(student_name, pre_survey_q9, post_survey_q9) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q9,
         "Post-Survey Response" = post_survey_q9)
```

```{r question 9 spring 2020}

reactable(spring_2020_pre_post_q9)
```

### Survey Question 10

I am prepared to justify my decisions related to assessment and treatment selection
```{r survey question 10 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q10 <- spring_2020 %>% 
  select(student_name, pre_survey_q10, post_survey_q10) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q10,
         "Post-Survey Response" = post_survey_q10)

```

```{r question 10 spring 2020}

reactable(spring_2020_pre_post_q10)
```

### Survcey Question 11

I am confident in my ability to apply principles of evidence-based practice to my assessment and treatment decisions
```{r survey question 11 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q11 <- spring_2020 %>% 
  select(student_name, pre_survey_q11, post_survey_q11) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q11,
         "Post-Survey Response" = post_survey_q11)

```

```{r question 11 spring 2020}

reactable(spring_2020_pre_post_q11)
```


### Survey Question 12

I am confident in my ability to make ‘online’ (in session) changes to my daily plans
```{r survey question 12 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q12 <- spring_2020 %>% 
  select(student_name, pre_survey_q12, post_survey_q12) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q12,
         "Post-Survey Response" = post_survey_q12)

```

```{r question 12 spring 2020}

reactable(spring_2020_pre_post_q12)
```


### Survey Question 13

I am knowledgeable about concussion management
```{r survey question 13 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q13 <- spring_2020 %>% 
  select(student_name, pre_survey_q13, post_survey_q13) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q13,
         "Post-Survey Response" = post_survey_q13)

```

```{r question 13 spring 2020}

reactable(spring_2020_pre_post_q13)
```

### Survey Question 14

I am comfortable working with clients with brain injuries
```{r survey question 14 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q14 <- spring_2020 %>% 
  select(student_name, pre_survey_q14, post_survey_q14) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q14,
         "Post-Survey Response" = post_survey_q14)

```

```{r question 14 spring 2020}

reactable(spring_2020_pre_post_q14)
```

### Survey Question 15

I am comfortable working with clients with awareness deficits
```{r survey question 15 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q15 <- spring_2020 %>% 
  select(student_name, pre_survey_q15, post_survey_q15) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q15,
         "Post-Survey Response" = post_survey_q15)

```

```{r question 15 spring 2020}

reactable(spring_2020_pre_post_q15)
```

### Survecy Question 16

I am able to use case history information (e.g., information about etiology) to guide my clinical decision making
```{r survey question 16 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q16 <- spring_2020 %>% 
  select(student_name, pre_survey_q16, post_survey_q16) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q16,
         "Post-Survey Response" = post_survey_q16)

```

```{r question 16 spring 2020}

reactable(spring_2020_pre_post_q16)
```

### Survey Question 17

I feel prepared to orally present cases
```{r survey question 17 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q17 <- spring_2020 %>% 
  select(student_name, pre_survey_q17, post_survey_q17) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q17,
         "Post-Survey Response" = post_survey_q17)

```

```{r question 17 spring 2020}

reactable(spring_2020_pre_post_q17)
```


### Survey Question 18

Training was systematic and well organized (Post-Survey Only)
```{r survey question 18 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q18 <- spring_2020 %>% 
  select(student_name, post_survey_q18) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q18)

```

```{r question 18 spring 2020}

reactable(spring_2020_pre_post_q18)
```

### Survey Question 19

Group meetings enhanced my learning (Post-Survey Only)
```{r survey question 19 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q19 <- spring_2020 %>% 
  select(student_name, post_survey_q19) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q19)

```

```{r question 19 spring 2020}

reactable(spring_2020_pre_post_q19)
```


### Survey Question 20

Group meetings were efficient (Post-Survey Only)
```{r survey question 20 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q20 <- spring_2020 %>% 
  select(student_name, post_survey_q20) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q20)

```

```{r question 20 spring 2020}

reactable(spring_2020_pre_post_q20)
```


### Survey Question 21

Group meetings exposed me to learning about other client profiles and case management techniques (Post-Survey Only)
```{r survey question 21 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q21 <- spring_2020 %>% 
  select(student_name, post_survey_q21) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q21)

```

```{r question 21 spring 2020}

reactable(spring_2020_pre_post_q21)
```


### Survey Question 22

I learned enough about treatment approaches implemented by my peers to be able to implement them with a client even though I never personally delivered the intervention (Post-Survey Only)
```{r survey question 22 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q22 <- spring_2020 %>% 
  select(student_name, post_survey_q22) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q22)

```

```{r question 22 spring 2020}

reactable(spring_2020_pre_post_q22)
```


### Survey Question 23

I was exposed to clients with the same disorder/diagnosis with different manifestations or treatment needs (Post-Survey Only)
```{r survey question 23 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q23 <- spring_2020 %>% 
  select(student_name, post_survey_q23) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q23)

```

```{r question 23 spring 2020}

reactable(spring_2020_pre_post_q23)
```

### Survey Question 24

My supervisor supported my case management and clinical approach (Post-Survey Only)
```{r survey question 24 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q24 <- spring_2020 %>% 
  select(student_name, post_survey_q24) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q24)

```

```{r question 24 spring 2020}

reactable(spring_2020_pre_post_q24)
```


### Survey Question 25

(If you have already taken cognitive rehabilitation course) Because of this clinical experience, I am now able to apply theoretical knowledge and principles in a clinically sound matter (Post-Survey Only)
```{r survey question 25 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q25 <- spring_2020 %>% 
  select(student_name, post_survey_q25) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q25)

```

```{r question 25 spring 2020}

reactable(spring_2020_pre_post_q25)
```


### Survey Question 26

(If you have already taken cognitive rehabilitation course) I had the appropriate knowledge of theories and practice from my coursework to apply to this clinical experience (Post-Survey Only)
```{r survey question 26 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q26 <- spring_2020 %>% 
  select(student_name, post_survey_q26) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q26)

```

```{r question 26 spring 2020}

reactable(spring_2020_pre_post_q26)
```


### Survey Question 27

(If you have not yet taken cognitive rehabilitation course) I feel more prepared about enrolling in class because of this clinical experience (Post-Survey Only)
```{r survey question 27 spring 2020 data cleaning, include=FALSE}

spring_2020_pre_post_q27 <- spring_2020 %>% 
  select(student_name, post_survey_q27) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q27)

```

```{r question 27 spring 2020}

reactable(spring_2020_pre_post_q27)
```