---
title: "BrICC Winter 2020 Student Data"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    source_code: embed
    vertical_layout: scroll
    theme: cerulean
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(rio)
library(here)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)

opts_chunk$set(echo = FALSE,
               fig.width = 5,
               fig.height = 6)

theme_set(theme_minimal(base_size = 8))

bricc <- import(here("data", "bricc_data_new.sav"),
               setclass = "tbl_df") %>% 
  characterize() %>% 
  janitor::clean_names() 

head(bricc)
```

# BrICC Quiz 


Column {.tabset data-width=650}
-----------------------------------------------------------------------

### Quiz Score Table Breakdown 
```{r total score data cleaning, include=FALSE}

score_table <- bricc %>% 
  select(student_name, 
         pre_test_total_score, 
         post_test_total_score, 
         pre_test_knowledge_score, 
         post_test_knowledge_score, 
         pre_test_application_score, 
         post_test_application_score) %>% 
  rename("Student Name" = student_name,
         "Pre-Test Total Score" = pre_test_total_score,
         "Post-Test Total Score" = post_test_total_score,
         "Pre-Test Knowledge Score" = pre_test_knowledge_score,
         "Post-Test Knowledge Score" = post_test_knowledge_score,
         "Pre-Test Application Score" = pre_test_application_score,
         "Post-Test Application Score" = post_test_application_score)

bricc_tidy_quiz <- bricc %>% 
  pivot_longer(
    cols = c(pre_test_total_score,
             post_test_total_score,
             pre_test_knowledge_score,
             post_test_knowledge_score,
             pre_test_application_score,
             post_test_application_score),
    names_to = "assessment",
    values_to = "score"
  )

```

```{r total score}

reactable(score_table)
```

### Quiz Score Plot Breakdown
```{r quiz plot data cleaning, include=FALSE}

bricc_tidy_quiz$assessment <- factor(bricc_tidy_quiz$assessment, 
                                     levels = c("pre_test_total_score",
                                                "post_test_total_score",
                                                "pre_test_knowledge_score",
                                                "post_test_knowledge_score",
                                                "pre_test_application_score",
                                                "post_test_application_score"))

```

```{r quiz plot, fig.width=7, fig.height=6.5}
ggplot(bricc_tidy_quiz, aes(assessment, score)) +
  geom_col(fill = "blue", 
           alpha = 0.7) +
  geom_text(aes(assessment, score, label = score),
            nudge_y = -0.5,
            color = "white") +
  facet_wrap(~student_name) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(color = "gray80")) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(plot.title = element_text(color = "black", size = 12, face = "bold", hjust = 0.5)) +
  labs(x = "",
       y = "Score",
       title = "BrICC Winter 2020 Student Scores") 
```


# BrICC Survey 

Column {.tabset data-width=650}
-----------------------------------------------------------------------

### Question 1

I am confident in my ability to conduct a consultation for the BrICC clinic

```{r survey question 1 data cleaning, include=FALSE}

pre_post_q1 <- bricc %>% 
  select(student_name, pre_survey_q1, post_survey_q1) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q1,
         "Post-Survey Response" = post_survey_q1)

```

```{r question 1}

reactable(pre_post_q1)
```


### Question 2

I am confident in my ability to administer standardized cognitive tests

```{r survey question 2 data cleaning, include=FALSE}

pre_post_q2 <- bricc %>% 
  select(student_name, pre_survey_q2, post_survey_q2) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q2,
         "Post-Survey Response" = post_survey_q2)

```

```{r question 2}

reactable(pre_post_q2)
```


### Question 3

I am confident in my ability to conduct a client-centered clinical interview

```{r survey question 3 data cleaning, include=FALSE}

pre_post_q3 <- bricc %>% 
  select(student_name, pre_survey_q3, post_survey_q3) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q3,
         "Post-Survey Response" = post_survey_q3)

```

```{r question 3}

reactable(pre_post_q3)
```

### Question 4

I am confident in my ability to identify treatment options to assist people with acquired cognitive impairments

```{r survey question 4 data cleaning, include=FALSE}

pre_post_q4 <- bricc %>% 
  select(student_name, pre_survey_q4, post_survey_q4) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q4,
         "Post-Survey Response" = post_survey_q4)

```

```{r question 4}

reactable(pre_post_q4)
```

### Question 5

I am prepared to write cognitive rehabilitation goals

```{r survey question 5 data cleaning, include=FALSE}

pre_post_q5 <- bricc %>% 
  select(student_name, pre_survey_q5, post_survey_q5) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q5,
         "Post-Survey Response" = post_survey_q5)

```

```{r question 5}

reactable(pre_post_q5)
```

### Question 6

I am prepared to administer direct interventions such as attention training or goal management training
```{r survey question 6 data cleaning, include=FALSE}

pre_post_q6 <- bricc %>% 
  select(student_name, pre_survey_q6, post_survey_q6) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q6,
         "Post-Survey Response" = post_survey_q6)

```

```{r question 6}

reactable(pre_post_q6)
```

### Question 7

I am prepared to engage in systematic instruction to support the use of external aids
```{r survey question 7 data cleaning, include=FALSE}

pre_post_q7 <- bricc %>% 
  select(student_name, pre_survey_q7, post_survey_q7) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q7,
         "Post-Survey Response" = post_survey_q7)

```

```{r question 7}

reactable(pre_post_q7)
```

### Question 8

I am prepared to engage in a needs assessment to identify cognitive strategies and support learning and use of them
```{r survey question 8 data cleaning, include=FALSE}

pre_post_q8 <- bricc %>% 
  select(student_name, pre_survey_q8, post_survey_q8) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q8,
         "Post-Survey Response" = post_survey_q8)

```

```{r question 8}

reactable(pre_post_q8)
```

### Question 9

I am confident in my ability to collect and analyze client session data
```{r survey question 9 data cleaning, include=FALSE}

pre_post_q9 <- bricc %>% 
  select(student_name, pre_survey_q9, post_survey_q9) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q9,
         "Post-Survey Response" = post_survey_q9)
```

```{r question 9}

reactable(pre_post_q9)
```

### Question 10

I am prepared to justify my decisions related to assessment and treatment selection
```{r survey question 10 data cleaning, include=FALSE}

pre_post_q10 <- bricc %>% 
  select(student_name, pre_survey_q10, post_survey_q10) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q10,
         "Post-Survey Response" = post_survey_q10)

```

```{r question 10}

reactable(pre_post_q10)
```

### Question 11

I am confident in my ability to apply principles of evidence-based practice to my assessment and treatment decisions
```{r survey question 11 data cleaning, include=FALSE}

pre_post_q11 <- bricc %>% 
  select(student_name, pre_survey_q11, post_survey_q11) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q11,
         "Post-Survey Response" = post_survey_q11)

```

```{r question 11}

reactable(pre_post_q11)
```


### Question 12

I am confident in my ability to make ‘online’ (in session) changes to my daily plans
```{r survey question 12 data cleaning, include=FALSE}

pre_post_q12 <- bricc %>% 
  select(student_name, pre_survey_q12, post_survey_q12) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q12,
         "Post-Survey Response" = post_survey_q12)

```

```{r question 12}

reactable(pre_post_q12)
```


### Question 13

I am knowledgeable about concussion management
```{r survey question 13 data cleaning, include=FALSE}

pre_post_q13 <- bricc %>% 
  select(student_name, pre_survey_q13, post_survey_q13) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q13,
         "Post-Survey Response" = post_survey_q13)

```

```{r question 13}

reactable(pre_post_q13)
```

### Question 14

I am comfortable working with clients with brain injuries
```{r survey question 14 data cleaning, include=FALSE}

pre_post_q14 <- bricc %>% 
  select(student_name, pre_survey_q14, post_survey_q14) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q14,
         "Post-Survey Response" = post_survey_q14)

```

```{r question 14}

reactable(pre_post_q14)
```

### Question 15

I am comfortable working with clients with awareness deficits
```{r survey question 15 data cleaning, include=FALSE}

pre_post_q15 <- bricc %>% 
  select(student_name, pre_survey_q15, post_survey_q15) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q15,
         "Post-Survey Response" = post_survey_q15)

```

```{r question 15}

reactable(pre_post_q15)
```

### Question 16

I am able to use case history information (e.g., information about etiology) to guide my clinical decision making
```{r survey question 16 data cleaning, include=FALSE}

pre_post_q16 <- bricc %>% 
  select(student_name, pre_survey_q16, post_survey_q16) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q16,
         "Post-Survey Response" = post_survey_q16)

```

```{r question 16}

reactable(pre_post_q16)
```

### Question 17

I feel prepared to orally present cases
```{r survey question 17 data cleaning, include=FALSE}

pre_post_q17 <- bricc %>% 
  select(student_name, pre_survey_q17, post_survey_q17) %>% 
  rename("Student Name" = student_name,
         "Pre-Survey Response" = pre_survey_q17,
         "Post-Survey Response" = post_survey_q17)

```

```{r question 17}

reactable(pre_post_q17)
```


### Question 18

Training was systematic and well organized (Post-Survey Only)
```{r survey question 18 data cleaning, include=FALSE}

pre_post_q18 <- bricc %>% 
  select(student_name, post_survey_q18) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q18)

```

```{r question 18}

reactable(pre_post_q18)
```

### Question 19

Group meetings enhanced my learning (Post-Survey Only)
```{r survey question 19 data cleaning, include=FALSE}

pre_post_q19 <- bricc %>% 
  select(student_name, post_survey_q19) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q19)

```

```{r question 19}

reactable(pre_post_q19)
```


### Question 20

Group meetings were efficient (Post-Survey Only)
```{r survey question 20 data cleaning, include=FALSE}

pre_post_q20 <- bricc %>% 
  select(student_name, post_survey_q20) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q20)

```

```{r question 20}

reactable(pre_post_q20)
```


### Question 21

Group meetings exposed me to learning about other client profiles and case management techniques (Post-Survey Only)
```{r survey question 21 data cleaning, include=FALSE}

pre_post_q21 <- bricc %>% 
  select(student_name, post_survey_q21) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q21)

```

```{r question 21}

reactable(pre_post_q21)
```


### Question 22

I learned enough about treatment approaches implemented by my peers to be able to implement them with a client even though I never personally delivered the intervention (Post-Survey Only)
```{r survey question 22 data cleaning, include=FALSE}

pre_post_q22 <- bricc %>% 
  select(student_name, post_survey_q22) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q22)

```

```{r question 22}

reactable(pre_post_q22)
```


### Question 23

I was exposed to clients with the same disorder/diagnosis with different manifestations or treatment needs (Post-Survey Only)
```{r survey question 23 data cleaning, include=FALSE}

pre_post_q23 <- bricc %>% 
  select(student_name, post_survey_q23) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q23)

```

```{r question 23}

reactable(pre_post_q23)
```

### Question 24

My supervisor supported my case management and clinical approach (Post-Survey Only)
```{r survey question 24 data cleaning, include=FALSE}

pre_post_q24 <- bricc %>% 
  select(student_name, post_survey_q24) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q24)

```

```{r question 24}

reactable(pre_post_q24)
```


### Question 25

(If you have already taken cognitive rehabilitation course) Because of this clinical experience, I am now able to apply theoretical knowledge and principles in a clinically sound matter (Post-Survey Only)
```{r survey question 25 data cleaning, include=FALSE}

pre_post_q25 <- bricc %>% 
  select(student_name, post_survey_q25) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q25)

```

```{r question 25}

reactable(pre_post_q25)
```


### Question 26

(If you have already taken cognitive rehabilitation course) I had the appropriate knowledge of theories and practice from my coursework to apply to this clinical experience (Post-Survey Only)
```{r survey question 26 data cleaning, include=FALSE}

pre_post_q26 <- bricc %>% 
  select(student_name, post_survey_q26) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q26)

```

```{r question 26}

reactable(pre_post_q26)
```


### Question 27

(If you have not yet taken cognitive rehabilitation course) I feel more prepared about enrolling in class because of this clinical experience (Post-Survey Only)
```{r survey question 27 data cleaning, include=FALSE}

pre_post_q27 <- bricc %>% 
  select(student_name, post_survey_q27) %>% 
  rename("Student Name" = student_name,
         "Post-Survey Response" = post_survey_q27)

```

```{r question 27}

reactable(pre_post_q27)
```